func-descr.template

### 2025-11-06 reports/capstone-movielens.site/02-3.OMR-model.Rmd
Capstone Report: `Overall Mean Rating (OMR) Model` sectioni updated.

If we predict all unknown ratings with $\hat{\mu}$, we obtain the following RMSE: 
```{r}
mu.MSEs <- naive_model_MSEs(mu)
data.frame(fold_No = 1:5, MSE = mu.MSEs) |>
  data.plot(title = "MSE resuls of the 5-fold CV method applied to the Overall Mean Rating Model",
              xname = "fold_No", 
              yname = "MSE")

@@

::: {.noteblock data-latex=""}
For the _Mean Squared Errors_ data visualization we use the custom data visualization function [data.plot](#func.data.plot) described in the [Data Helper Functions](#appndx_a.data_helper.functions) section of the [Appendix] to this report, which is defined in the [Data Visualization](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/data.helper.functions.R#L447) section of the [data.helper.functions.R](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/data.helper.functions.R#L592) script on _GitHub_.
:::

Here we also used [naive_model_MSEs](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/common-helper.functions.R#L89) function defined in the [common-helper.functions.R](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/common-helper.functions.R#L89) script (already mentioned above) to compute _Mean Squared Errors_ using _5-Fold Cross Validation_ method:

```{r eval=FALSE }
naive_model_MSEs <- function(val) {
  sapply(edx_CV, function(cv_item){
    mse(cv_item$validation_set$rating - val)
  })
}
```

One more function, defined in the [same script](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/common-helper.functions.R#L94), that we will need for further analysis of the current model, is the [naive_model_RMSE](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/common-helper.functions.R#L94) one:
```{r eval=FALSE }
naive_model_RMSE <- function(val){
  sqrt(mean(naive_model_MSEs(val)))
}
```
\newpage

@@

If we plug in any other number, we will get a higher RMSE. Let's prove that by the following small investigation:
```{r }
  deviation <- seq(0, 6, 0.1) - 3

@@

@@

print_log1("Is the previously computed RMSE the best for the current model: %1",
         mu.RMSE == min_rmse)
```
```{r eval=FALSE}
RMSEs.ResultTibble.OMR <- RMSEs.ResultTibble |> 
  RMSEs.AddRow("Overall Mean Rating Model", mu.RMSE)
```
```{r}
RMSE_kable(RMSEs.ResultTibble.OMR)
```

::: {.noteblock data-latex=""}
Here use the [RMSEs.AddRow](#func.RMSEs.AddRow) and [RMSE_kable](#func.RMSE_kable) functions described in the [Common Helper Functions: Result RMSEs Table] section of the [Appendix] to this report.
:::

>>>>

If we predict all unknown ratings with $\hat{\mu}$, we can obtain RMSE as follows:: 
```{r}
mu.MSEs <- naive_model_MSEs(mu)
data.frame(fold_No = 1:5, MSE = mu.MSEs) |>
  data.plot(title = "MSE resuls of the 5-fold CV method applied to the Overall Mean Rating Model",
              xname = "fold_No", 
              yname = "MSE")

@@

::: {.noteblock data-latex=""}

The following custom functions described in [Appendix A: Support Functions] of *this Report*, are used in the code snippets above:

  - [naive_model_MSEs](#func.naive_model_MSEs) (described in section [Overall Mean Rating (OMR) Model Helper Functions]) to compute _Mean Squared Errors_ using _5-Fold Cross Validation_ method;

  - [data.plot](#func.data.plot) (described in section [Data Visualization Functions]) for the _Mean Squared Errors_ data visualization.

:::

@@

If we plug in any other number, we will get a higher *RMSE*. Let's prove that by the following small investigation:
```{r }
  deviation <- seq(0, 6, 0.1) - 3

@@

::: {.noteblock data-latex=""}
In the code snippet above, we use the custom function [naive_model_RMSE](#func.naive_model_RMSE) described in the [Overall Mean Rating (OMR) Model Helper Functions] section of [Appendix A: Support Functions] to calculate *RMSEs* for the sequence of the deviation values.
:::

@@

print_log1("Is the previously computed RMSE the best for the current model: %1",
         mu.RMSE == min_rmse)
```

::: {.noteblock data-latex=""}
To print the log, we use the custom function [print_log1](#func.print_log1) described in the [Logging Functions] section of [Appendix A: Support Functions].
:::

```{r eval=FALSE}
RMSEs.ResultTibble.OMR <- RMSEs.ResultTibble |> 
  RMSEs.AddRow("Overall Mean Rating Model", mu.RMSE)
```
```{r}
RMSE_kable(RMSEs.ResultTibble.OMR)
```

::: {.noteblock data-latex=""}
To print the table above, we use the [RMSEs.AddRow](#func.RMSEs.AddRow) and [RMSE_kable](#func.RMSE_kable) custom functions described in the [Result RMSEs Tibble Functions] section of [Appendix A: Support Functions].
:::

### 2025-11-06 reports/capstone-movielens.site/05.appendix.Rmd
Capstone Report: `Overall Mean Rating (OMR) Model` sectioni updated.

### Overal Mean Rating (OMR) Model Functions
\

@@

#### [@@func](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/@@script.R#LX) Function {#func.@@func}
\

::: { #func.@@func.usage .sidebar }
##### Usage
\

```{r eval=FALSE}
@@func()

@@

::: { #func.@@func.args .sidebar }
##### Arguments
\

::: { #func.@@func.args. .sidebar }
  - **x:** ;

::: { #func.@@func.details .sidebar }
##### Details
\

::: { #func.@@func.value .sidebar }
##### Value
\

::: { #func.@@func.code .sidebar }
##### Source Code
\

The source code of the [@@func](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/@@script.R#LX) function is shown below:
```{r eval=FALSE}
```

::: {.noteblock data-latex=""}
The source code of the [@@func](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/data.helper.functions.R#LX) function is also available in the [@@script.R](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/@@script.R#LX) script on _GitHub_.
:::
:::

@@

# End of Report -------------------------------------------------------------
v

>>>>

### Overall Mean Rating (OMR) Model Helper Functions
\

@@

#### [naive_model_MSEs](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/OMR-model.functions.R#L2) Function {#func.naive_model_MSEs}
\

Calculates the Mean Squared Errors (MSEs) for the *Overall Mean Rating (OMR) Model* using the *K-Fold Cross Validation* method as described in section [OMR Model Building] of *this Report*.

::: { #func.naive_model_MSEs.usage .sidebar }
##### Usage
\

```{r eval=FALSE}
mu <- mean(edx$rating)
mu.MSEs <- naive_model_MSEs(mu)

@@

::: { #func.naive_model_MSEs.args .sidebar }
##### Arguments
\

::: { #func.naive_model_MSEs.args. .sidebar }
  - **mu:** The overall mean rating value.

::: { #func.naive_model_MSEs.value .sidebar }
##### Value
\

The Mean Squared Errors (MSEs) values obtained from applying the *K-Fold Cross-Validation* method to the *Overall Average Rating (OMR) Model*.
:::

::: { #func.naive_model_MSEs.code .sidebar }
##### Source Code
\

The source code of the [naive_model_MSEs](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/OMR-model.functions.R#L2) function is shown below:
```{r eval=FALSE}
naive_model_MSEs <- function(mu) {
  sapply(edx_CV, function(cv_item){
    mse(cv_item$validation_set$rating - mu)
  })
}
```

::: {.noteblock data-latex=""}
The source code of the [naive_model_MSEs](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/data.helper.functions.R#L2) function is defined in the [OMR-model.functions.R](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/OMR-model.functions.R#L2) script on _GitHub_.
:::
:::

#### [naive_model_RMSE](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/OMR-model.functions.R#L7) Function {#func.naive_model_RMSE}
\
Calculates the Root Mean Squared Error (RMSE) for the *Overall Mean Rating (OMR) Model* using the *K-Fold Cross Validation* method as described in section [OMR Model Building] of *this Report*.

::: { #func.naive_model_RMSE.usage .sidebar }
##### Usage
\

```{r eval=FALSE}
mu <- mean(edx$rating)
mu.RMSE <- naive_model_RMSE(mu)
```
:::

::: { #func.naive_model_RMSE.args .sidebar }
##### Arguments
\

::: { #func.naive_model_RMSE.args. .sidebar }
  - **mu:** The overall mean rating value.

::: { #func.naive_model_RMSE.details .sidebar }
##### Details
\

This function internally calls the [naive_model_MSEs](#func.naive_model_MSEs) function described above.
:::

::: { #func.naive_model_RMSE.value .sidebar }
##### Value
\

The Root Mean Squared Errors (RMSE) value obtained from applying the *K-Fold Cross-Validation* method to the *Overall Average Rating (OMR) Model*.
:::

::: { #func.naive_model_RMSE.code .sidebar }
##### Source Code
\

The source code of the [naive_model_RMSE](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/OMR-model.functions.R#L7) function is shown below:
```{r eval=FALSE}
naive_model_RMSE <- function(mu){
  sqrt(mean(naive_model_MSEs(mu)))
}
```

::: {.noteblock data-latex=""}
The source code of the [naive_model_RMSE](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/data.helper.functions.R#L7) function is defined in the [OMR-model.functions.R](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/OMR-model.functions.R#L7) script on _GitHub_.
:::
:::

@@

### 2025-11-06 reports/capstone-movielens.site/work/func-descr.template.Rmd
Capstone Report: `Overall Mean Rating (OMR) Model` sectioni updated.

>>>>

### Overal Mean Rating (OMR) Model Functions
\

::: {.noteblock data-latex=""}
The complete source code of the functions described in this section is available in the [OMR-model.functions.R](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/OMR-model.functions.R) script on _GitHub_.
:::

#### [OMR_model_func.tmpl](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/OMR-model.functions.R#LX) Function {#func.OMR_model_func.tmpl}
\

::: { #func.OMR_model_func.tmpl.usage .sidebar }
##### Usage
\

```{r eval=FALSE}
OMR_model_func.tmpl()

::: { #func.OMR_model_func.tmpl.args .sidebar }
##### Arguments
\

::: { #func.OMR_model_func.tmpl.args. .sidebar }
  - **x:** ;

::: { #func.OMR_model_func.tmpl.details .sidebar }
##### Details
\

::: { #func.OMR_model_func.tmpl.value .sidebar }
##### Value
\

::: { #func.OMR_model_func.tmpl.code .sidebar }
##### Source Code
\

The source code of the [OMR_model_func.tmpl](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/OMR-model.functions.R#LX) function is shown below:
```{r eval=FALSE}
```

::: {.noteblock data-latex=""}
The source code of the [OMR_model_func.tmpl](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/data.helper.functions.R#LX) function is defined in the [OMR-model.functions.R](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/OMR-model.functions.R#LX) script on _GitHub_.
:::
:::
